Multi-Index and Multi-Level Monte Carlo Evaluation of HJM Models

### 2016-05-07 tests/HJM/manuscript.tex
complete pics 2 redo

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{weakerr3.pdf}
        %\caption{A gull}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{strongerr3.pdf}
        %\caption{A tiger}
    \end{subfigure}
    \caption{\label{img:rateFig3} Weak (left) and strong (right) error
    for the temporal discretisation
    $\nnorm{\Psi_{2N_f}-\Psi_{N_f}}{}$.}
\end{figure}

@@

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{weakerr4.pdf}
        %\caption{A gull}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{strongerr4.pdf}
        %\caption{A tiger}
    \end{subfigure}
    \caption{\label{img:rateFig3} Above: Weak (left) and strong (right) error
    for the temporal discretisation
    $\nnorm{\overline G_{65,2N_f}-\overline G_{65,N_f}}{}$,
    along with the $N_f^{-\frac{3}{2}}$ and $N_f^{3}$ reference lines (red).}
\end{figure}

>>>>

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{weakerr3.pdf}
        %\caption{A gull}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{strongerr3.pdf}
        %\caption{A tiger}
    \end{subfigure}
    \caption{\label{img:rateFig3} Weak (left) and strong (right) error
    for frequency cutoff
    $\nnorm{\Psi_{2N_f}-\Psi_{N_f}}{}$.}
\end{figure}

@@

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{weakerr4.pdf}
        %\caption{A gull}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{strongerr4.pdf}
        %\caption{A tiger}
    \end{subfigure}
    \\
        \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{weakerr5.pdf}
        %\caption{A gull}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{strongerr5.pdf}
        %\caption{A tiger}
    \end{subfigure}
    \caption{\label{img:rateFig3} Above: Weak (left) and strong (right) error
    for the cutoff
    $\nnorm{\overline G_{65,2N_f}-\overline G_{65,N_f}}{}$,
    along with the $N_f^{-\frac{3}{2}}$ and $N_f^{3}$ reference lines (red).
    Below: Weak (left) and strong (right) error for the temporal discretisation
    $\nnorm{\overline G_{2N_t-1,16} - \overline G_{N_t,16}}{}$ with the 
    $N_t^{-1}$ and $N_t^{-2}$ reference lines for the weak and strong error,
    respectively (red).}
\end{figure}
